### 2023-12-29 tesis_Ashish/Chapter7/chapter7.tex
Updated thesis 29 Dec 2023

Statistical precision is another uncertainty that need to be considered for precise luminosity measurement. It must be kept minimal to achieve 1 $\%$ accuracy for HL-LHC luminosity measurement.

Relative statistical uncertainty in $\%$ = $\frac{\sqrt{N}}{N} \times 100$ \\

where N = (Number of counts per event)$\times$(Trigger Frequency)$\times$(Time Integration period).

@@

\section{Conclusion}

@@

>>>>

Statistical precision is another uncertainty that need to be considered for precise luminosity measurement. It must be kept minimal to achieve 1 $\%$ accuracy for HL-LHC luminosity measurement. Relative statistical uncertainty in $\%$ = $\frac{\sqrt{N}}{N} \times 100$ where N is the product of the number of counts per event, the trigger frequency and the time integration period.\\

@@

\section{Summmary}

@@

Chapter 1 of the thesis lays the groundwork for understanding collider experiments, focusing on the critical role of luminosity in particle physics, particularly in the Large Hadron Collider (LHC). Collider experiments, crucial for probing the fundamental nature of matter, involve high-energy collisions, such as those between protons or electrons. Luminosity, indicating the collision rate, is essential for determining particle production rates and detecting rare events. Accurate luminosity measurement is imperative as it directly influences the rate of particle production, crucial for significant discoveries like the Higgs boson and precise measurements of particles like the top quark. The chapter highlights ongoing advancements in enhancing luminosity measurement precision, notably through the CMS's pixel detector, which is key to improving particle property measurements and discovering new physics beyond the Standard Model.

In Chapter 2, we delves into the comprehensive strategies and methodologies adopted in the CMS experiment for luminosity measurement. We elaborates on the Pixel Cluster Counting (PCC) method's precision and how it is optimized for high luminosity scenarios anticipated in future LHC runs. The chapter also discusses the advancements in the PCC technique, including the development of algorithms and the calibration processes that will be imperative for maintaining measurement accuracy in the High-Luminosity LHC (HL-LHC) phase. The innovations in the detector technology, data processing, and analysis underscore the ongoing evolution of the CMS experiment's capabilities to achieve precise and reliable luminosity measurements.

In Chapter 3, we discuss the calibration of luminosity measurement devices using the van der Meer (vdM) scan method. It explains the technique developed by Simon van der Meer for relating the detection rate of a luminometer to absolute luminosity. This involves scanning colliding beams across each other and measuring the beam overlap integral, which is proportional to luminosity. The chapter also covers background estimation to account for various sources of noise and the Poly2G model, a fitting function used in the vdM calibration process.

In Chapter 4, the results from the CMS experiment at the Large Hadron Collider's Run 2 are comprehensively detailed. For the year 2018, the integrated luminosity was calculated to be \(60.47 \, \text{fb}^{-1}\). The visible cross section was accurately determined as \(960.54 \pm 0.85 \, (\text{stat.}) \, \text{mb}\). A total of 155 good pixel modules were selected for the final luminosity measurement. Systematic uncertainties were meticulously quantified, including afterglow (\(0.3\%\)), linearity (\(0.4\%\)), and cross detector stability (\(0.3\%\)), contributing to a total uncertainty of \(1.08\%\).

In Chapter 5, significant results from the PCC luminosity measurement during its third run are outlined. The chapter reports that the PCC integrated luminosity for 2022 was computed to be \(38.61 \, \text{fb}^{-1}\) . Furthermore, a comprehensive analysis of systematic uncertainties in the luminosity measurement for the year 2022 is presented. These uncertainties encompass a range of factors including calibration (1.3\%), integration (0.8\%), and other specific sources such as beam current (0.2\%), orbit drift (0.3\%), and cross-detector linearity (0.54\%), culminating in a total uncertainty of \(1.5\%\).

Chapter 6 of the thesis on the TEPX luminometer for the High Luminosity Large Hadron Collider (HL-LHC) addresses the challenges and solutions in luminosity measurement for the anticipated HL-LHC phase starting in 2029. With the HL-LHC set to increase instantaneous luminosity to up to 200 proton-proton collisions per bunch crossing, the TEPX luminometer is designed for high-precision, real-time measurement using pixel cluster counting and coincidence counting. This setup enhances accuracy and handles the expected increase in radiation levels, data rates, and event complexity. The TEPX system is noted for its linearity, indicating its effectiveness as a luminometer as the PCC visible cross section remains constant across various luminosity levels. Advanced algorithms using dr and $d\phi$ variables effectively manage non-linearity and suppress fake coincidences at high pileup levels, maintaining non-linearity within 1\% across the pileup range. Furthermore, the system achieves high efficiency and low fake rates in complex luminosity conditions. Statistical precision is also emphasized as a critical factor for achieving the targeted 0.1\% accuracy in HL-LHC luminosity measurements.
